Quick, Draw! Image Classification

### 2018-12-08 report/draft.tex
latest changes

A slight (~5\%) improvement in the accuracy of a CNN when compared to a fully
connected network, keeping the number of parameters constant, was observed.
However, the CNN happened to be around 13 times faster in practice. This
delta in accuracy and speed is likely to be amplified as we scale the model
up with respect to model complexity or data.

@@

We are able to confirm that adding data to the minority class to reduce
class imbalance increases prediction accuracy. Figure \ref{fig:h4Results}
shows results that support this assertion by gradually decreasing the class
imbalance by increasing the number of samples within the minority class.
Minority class accuracy ranged from 43\% with a 1:500 class imbalance to
98\% with a 1:1 class imbalance.These predictions were based on 20,000 total
samples which were previously unseen. The neural network models we
tested tended to generalize well on the most important weights, while
attempting to classify only the minority categories.

@@

Results for various number of classes $k$ are visualized in the Appendix
under Figure \ref{fig:h5Results}. Results for various amounts of training
data are under Figure \ref{fig:h6Results} in the Appendix. It can be
interpreted from the regression that for every additional category,
we can expect the test accuracy go down by 1.88\% and test loss to go up by
6.4\% while for every additional datapoint, we can expect the accuracy to go
up by .0016\% and loss to go down by .0056\%. Both results are statistically
significant with reasonably tight confidence intervals and standard errors.

>>>>

We found a slight (~5\%) improvement in the accuracy of a CNN when compared
to a similarly parameterized fully connected neural network. However, training
time for the CNN was about 13 times faster in practice. The difference in
accuracy and speed is likely to be amplified as we scale the model up in
respect to complexity of amount of data.

@@

We are able to confirm that adding data to the minority class to reduce
class imbalance increases prediction accuracy. Figure \ref{fig:h4Results}
shows results that support this assertion by gradually decreasing the class
imbalance by increasing the number of samples within the minority class.
Minority class accuracy ranged from 43\% with a 1:500 class imbalance to
98\% with a 1:1 class imbalance.These predictions were based on 20,000 total
samples which were previously unseen. Neural network models tend to
generalize well on the most important weights, while attempting to classify
only the minority categories.

@@

Results for various number of classes $k$ are visualized in the Appendix
under Figure \ref{fig:h5Results}. Results for various amounts of training
data are under Figure \ref{fig:h6Results} in the Appendix. It can be
interpreted from the regression that for every additional category,
we can expect the test accuracy go down by 1.88\% and test loss to go up by
6.4\% while for every additional datapoint, we can expect the accuracy to go
up by 0.0016\% and loss to go down by 0.0056\%. Both results are statistically
significant with reasonably tight confidence intervals and standard errors.
